---
title: "toronto vs. IL"
author: "SB"
date: "Wednesday, February 04, 2015"
output: pdf_document
---

# graphing IL from Toronto example

## may 7, 2017

modify the toronto example to use the 
Israeli data
## load setup code, simulate thesis state 
```{r setup}
library(RColorBrewer)
library(maptools)
library(ggmap)
library(rgeos)
library(censusFunctions) 

setwd("/Volumes/Bmac/febThesis/index")
ilmap <- importData("savedGoogleMap")
# Read the neighborhood shapefile data and plot
setwd("~/scratch/toronto_neighbourhoods")
shpfile <- "NEIGHBORHOODS_WGS84_2.shp"
sh <- rgdal::readOGR(shpfile)
plot(sh)

# Add demographic data
# The neighbourhood ID is a string - change it to a integer
sh@data$AREA_S_CD <- as.numeric(sh@data$AREA_S_CD)

# Read in the demographic data and merge on Neighbourhood Id
demo <- read.csv(file="WB-Demographics.csv", header=T)
sh2 <- merge(sh, demo, by.x='AREA_S_CD', by.y='Neighbourhood.Id')


```
now, what does this col=cols line do?


```{r second}


# Set the palette
# creates 128 shades between white and red
p <- colorRampPalette(c("white", "red"))(128)
palette(p)

# Scale the total population to the palette
pop <- sh2@data$Total.Population
cols <- (pop - min(pop))/diff(range(pop))*127+1
# what is this cols variable?
# View(cols) #don't call view in ess, only Rstudio'
pop  # city-section populations range from 7k to 50k
cols[1]
range(cols)
## pop[12]
## # what column names are there?
## names(sh2@data)
## ```
## What is the population of the 12th area?
## ```{r pop1}
## #ggmap(ilmap)
## pop[12]
## ```
## What is the name of that area?
## ```{r nme}
## sh2@data$AREA_NAME[12]
## ```
## Does this area have any aliases?
## ```{r rco}
## sh2@data$Neighbourhood[12]
```

### Can you say any of that with inline code?
The population of region `r sh2@data$AREA_NAME[12]` aka
`r sh2@data$Neighbourhood[12]` was `r pop[12]` in 1998.
By 2010 it had fallen to `r pop[22]`.
This paragraph is interesting because, blah.
 
```{r help}
chngDir("index")
polygon <- sf::st_read("../includes/ISR_adm/ISR_adm1.shp")
points <- fortify(polygon)
ilpoints <- fortify(polygon, region = "NAME_1")
levels(polygon$NAME_1)
avgage <- c(10, 11, 15, 20.3, 31, 11, 4)
avgage[3]
# fake data, range 0-40
frame_il <- data.frame( region = levels(polygon$NAME_1), age = as.numeric(unlist(avgage)), stringsAsFactors = FALSE)
colnames(frame_il) 

frame_il[[2]]
typeof(frame_il[[2]])
# make palette with 40 levels
pal <-  colorRampPalette(brewer.pal(11, "Spectral"))(40)
# no place will be dark red, my data only goes to 31
palette(rev(p))
## scale
age <- frame_il$age 
# this gives an error, age is still not numeric
range(age)
age

colours <- (age - min(age)) / diff(range(age)) * 40
colours
## merge - currently I only have the region names, need the shape-polygons
## can these be merged?
ilpoints$NAME_1
## is the same as?
frame_il$region <- as.factor(frame_il$region)

frame_ils <- merge(frame_il, ilpoints,
                   by.x = 'region',
                   by.y = 'NAME_1')

## try other package
install_github("arilamstein/choroplethr")
install_github("choroplethrAdmin1", "arilamstein")
library(choroplethr)
library(choroplethrAdmin1)
## help page http://www.arilamstein.com/open-source/choroplethr/creating-administrative-level-1-maps/
?df_japan_census
head(df_japan_census)
## is the country available?
#get_admin1_regions("japan")
#get_admin1_regions("china")
get_admin1_regions("israel")
```
## those are the regions available to map, 
Only has 6 regions, seems to lack Golan and Krayot Haifa regions I need.
## what region do i still need to add?

```{r moerle}
admin1_map("japan")
admin1_map("china")
admin1_map("israel")

# grab two columns
#japs <-read.table(text = "", ...)
## japs <- data.frame(region = character(),
##                   value  = numeric(),
##                    stringsAsFactors = FALSE)
df_japan_census$value <- df_japan_census$pop_2010
## plot
admin1_choropleth(country.name = "japan",
                  df = df_japan_census,
                  title = "2010 Japan Population Estimates",
                  num_colors = 1)
```
zoom in on a region 
```{r exmg}
kansai = c("mie", "nara", "wakayama", "kyoto", "osaka", "hyogo", "shiga")
admin1_choropleth(country.name = "japan",
                  df           = df_japan_census,
                  title        = "2010 Japan Population Estimates - Kansai Region",
                  legend       = "Population",
                  num_colors   = 1,
                  zoom         = kansai)
```
but surely this doesn't work for israel?
```{r suly}
?df_israel
#plot(frame_ils, col <- colours )

# Scale the total population to the palette
pop <- sh2@data$Total.Population
cols <- (pop - min(pop))/diff(range(pop))*127+1

## stuff
demo
typeof(demo)
typeof(frame_il)
```



```{r more}
plot(sh, col = cols)

#RColorBrewer, spectral
p <- colorRampPalette(brewer.pal(11, 'Spectral'))(128)
palette(rev(p))
plot(sh2, col = cols)

#GGPLOT 
points <- fortify(sh, region = 'AREA_S_CD')

# Plot the neighborhoods
toronto <- qmap("Toronto, Ontario", zoom = 10)
toronto + geom_polygon(aes(x=long,y=lat, group=group, alpha=0.25), data=points, fill='white') + geom_polygon(aes(x=long,y=lat, group=group), data=points, color='black', fill=NA)

# merge the shapefile data with the social housing data, using the neighborhood ID
points2 <- merge(points, demo, by.x='id', by.y='Neighbourhood.Id', all.x=TRUE)

# Plot
toronto + geom_polygon(aes(x=long,y=lat, group=group, fill=Total.Population), data=points2, color='black') + 
  scale_fill_gradient(low='white', high='red')

# Spectral plot
toronto + geom_polygon(aes(x=long,y=lat, group=group, fill=Total.Population), data=points2, color='black') + 
  scale_fill_distiller(palette='Spectral') + scale_alpha(range=c(0.5,0.5))
```
